---
title: "README"
output: html_document
---

# check_balance

This R package includes a function (```check_balance```) that returns a descriptive table summarizing the descriptive statistics for two groups, allowing users to conduct group comparisons when needed.

### Purpose

The goal of this function is to summarize and compare descriptive statistics between two groups, allowing users to check baseline equivalence, identify potential confounders, and detect outliers or unexpected distributions. It is designed to support data-driven decision-making and enhance transparency in comparative analyses.

### Function Description

Given a dataset with two groups (e.g., data from a case-control study), ```check_balance``` outputs a descriptive table summarizing the mean of each group, the difference in means between the groups, the test statistic from either a Pearson's chi-squared test or Fisher’s exact test, the corresponding p-value, and the confidence interval. The function is designed to assess whether there are statistically significant differences in group means.

### R Installation Instructions

```{r}
install.packages("devtools") 
library(devtools)
devtools::install_github("leiyang0321/check.balance")
library(check.balance)
```

### Example

For instance, ```check_balance``` can be used to identify differences in the means of all predictors (or explanatory variables) between two groups, and to perform either Pearson’s chi-squared test or Fisher’s exact test to compute the corresponding test statistics and p-values.

```{r}
check_balance(data = lalonde,
              treatment = "treat",
              num = c("age", "educ"),
              cat = c("race", "married"),
              round = 3)
```



